DATA 621 Homework #3

### 2019-10-30 hw3/HW3.Rmd
Fixed a mistake

```{r}
str(train)
str(test)
## try it out 
train <- density_diff(train,test,"nox",train$target,"nox_density")$new_data_training
train <- density_diff(train,test,"age",train$target,"age_density")$new_data_training 
train <- density_diff(train,test,"indus",train$target,"indus_density")$new_data_training
train <- density_diff(train,test,"dis",train$target,"dis_density")$new_data_training
train <- density_diff(train,test,"rad",train$target,"rad_density")$new_data_training
train <- density_diff(train,test,"tax",train$target,"tax_density")$new_data_training
train <- density_diff(train,test,"ptratio",train$target,"ptratio_density")$new_data_training
train <- density_diff(train,test,"lstat",train$target,"lstat_density")$new_data_training
train <- density_diff(train,test,"medv",train$target,"medv_density")$new_data_training

test<- density_diff(train,test,"nox",train$target,"nox_density")$new_data_eval
test<- density_diff(train,test,"age",train$target,"age_density")$new_data_training 
test<- density_diff(train,test,"indus",train$target,"indus_density")$new_data_training
test<- density_diff(train,test,"dis",train$target,"dis_density")$new_data_training
test<- density_diff(train,test,"rad",train$target,"rad_density")$new_data_training
test<- density_diff(train,test,"tax",train$target,"tax_density")$new_data_training
test<- density_diff(train,test,"ptratio",train$target,"ptratio_density")$new_data_training
test<- density_diff(train,test,"lstat",train$target,"lstat_density")$new_data_training
test<- density_diff(train,test,"medv",train$target,"medv_density")$new_data_training

>>>>

```{r}
str(train)
str(test)
## try it out 
train <- density_diff(train,test,"nox",train$target,"nox_density")$new_data_training
train <- density_diff(train,test,"age",train$target,"age_density")$new_data_training 
train <- density_diff(train,test,"indus",train$target,"indus_density")$new_data_training
train <- density_diff(train,test,"dis",train$target,"dis_density")$new_data_training
train <- density_diff(train,test,"rad",train$target,"rad_density")$new_data_training
train <- density_diff(train,test,"tax",train$target,"tax_density")$new_data_training
train <- density_diff(train,test,"ptratio",train$target,"ptratio_density")$new_data_training
train <- density_diff(train,test,"lstat",train$target,"lstat_density")$new_data_training
train <- density_diff(train,test,"medv",train$target,"medv_density")$new_data_training
train <- density_diff(train,test,"rm",train$target,"rm_density")$new_data_training
train <- density_diff(train,test,"zn",train$target,"zn_density")$new_data_training

test<- density_diff(train,test,"nox",train$target,"nox_density")$new_data_eval
test<- density_diff(train,test,"age",train$target,"age_density")$new_data_eval
test<- density_diff(train,test,"indus",train$target,"indus_density")$new_data_eval
test<- density_diff(train,test,"dis",train$target,"dis_density")$new_data_eval
test<- density_diff(train,test,"rad",train$target,"rad_density")$new_data_eval
test<- density_diff(train,test,"tax",train$target,"tax_density")$new_data_eval
test<- density_diff(train,test,"ptratio",train$target,"ptratio_density")$new_data_eval
test<- density_diff(train,test,"lstat",train$target,"lstat_density")$new_data_eval
test<- density_diff(train,test,"medv",train$target,"medv_density")$new_data_eval
test<- density_diff(train,test,"rm",train$target,"rm_density")$new_data_eval
test<- density_diff(train,test,"zn",train$target,"zn_density")$new_data_eval
